The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs

### 2022-03-11 src/paper/results/robustness_to_sensitivity_assumptions.tex
Add missing word.
Co-authored-by: Janos Gabler <janos.gabler@gmail.com>
Implmeent Klara's suggestions from zulip.

    This section shows that our results are robust to making less favorable assumptions
    on rapid test sensitivity. We proceed by describing several possible ways of
    calibrating rapid test sensitivity profiles based on recent studies. Since none of
    these methods is inherently better than the others, we make simulations with two
    sensitivity profiles: The average over all methods and the lower envelope over all
    methods.

@@

    % Describe sensitivity lookupd vs. interpolation
    For the mapping of $Ct$ values to rapid test sensitivities, again we have two
    options. First, we can simply look up the discretized values for the three $Ct$
    provided in \cite{Scheiblauer2021} (below 20, 25 to 30 and above 35). Secondly, we
    can use linear regression to estimate a continous mapping for the relationship by
    assuming that the $Ct$ values of each bin are achieved exactly at the bin midpoints
    and that the relationship is linear.

@@

    Figure \ref{fig:sensitivity_assumptions} shows that the updated sensitivity
    estimates are lower than the ones used for our original results, especially towards
    the end of an infection. However, the main results barely change. This is due to the
    fact that the differences are most important towards the later stage of an
    infection. Uncovering an infection that was previously undetected at that stage does
    not have a large effect on infection dynamics.

>>>>

    This section shows that our results are robust to making less favorable assumptions
    on rapid test sensitivity. We proceed by describing several possible ways of
    calibrating rapid test sensitivity profiles based on recent studies. Since none of
    these methods is inherently better than the others, we make simulations with two
    sensitivity profiles: The average over all methods and the lower envelope over all
    methods using recent studies.

@@

    % Describe sensitivity lookupd vs. interpolation
    For the mapping of $Ct$ values to rapid test sensitivities, again we have two
    options. First, we can simply look up the discretized values for the three $Ct$ bins
    provided in \cite{Scheiblauer2021} (below 20, 25 to 30 and above 35). Secondly, we
    can use linear regression to estimate a continous mapping for the relationship by
    assuming that the $Ct$ values of each bin are achieved exactly at the bin midpoints
    and that the relationship is linear.

@@

    Figure \ref{fig:sensitivity_assumptions} shows that the updated sensitivity
    estimates are lower than the ones used for our original results, especially towards
    the end of an infection. However, the main results barely change. This is due to the
    fact that the differences are largest towards the later stage of an
    infection. Uncovering an infection that was previously undetected at that stage does
    not have a large effect on infection dynamics.

### 2022-03-11 src/rev1_reply_comments.tex
Implmeent Klara's suggestions from zulip.

@@

              Furthermore, note that we only use the pre-pandemic diary data as the
              starting point. Contact restrictions and individual behavior adjustments
              reduce contacts. These are active throughout the period of analysis and
              they vary with the strictness of measure. In order to do so, it is crucial
              to take the type of contact into account; see for example our analysis of
              potential school closures on Page~\pageref{ref.2.a}. Closed schools mean
              that children have far fewer and parents have somewhat fewer contacts than
              without school closures.

@@

              We base our assumption on infectiousness being independent of age on
              \citet{Jones2021}. That study was the only one we could find that was able
              differentiated between age differences in susceptibility (given a risk
              contact) vs. age differences in contact patterns. Moreover, they had fine
              grained age bins. That paper reports only slight differences in viral
              loads between German adults and children: ``The least infectious youngest
              children have 78\% (61, 94) of the peak culture probability of adults aged
              45 to 55''. Furthermore, they caution that these lower numbers may be due
              to different sample taking---such as the usage of smaller pediatric swab
              devices---rather than actual lower viral loads and conclude that the
              differences, if existent, are likely not clinically relevant. In fact,
              \citet{Goldstein2021}  reach similar conclusions, writing: \textit{``There
                  is limited evidence in the literature regarding age-related differences in
                  infectivity, although point estimates in several studies suggest that
                  infectivity may increase somewhat with age.''} We are thus confident that
              different assumptions in the range of plausible values would not be
              to change our results in a quantitatively meaningful way.

@@

              In our model, we thus simplify the way vaccines reduce transmission risk.
              In particular, we assume that that 75\% of individuals achieve sterile
              immunity through a vaccination while the remaining 25\% remain fully
              susceptible. SFirstly, the existing evidence supports the
              assumption that all four vaccines approved in the EU (Biontech/Pfizer,
              Moderna, AstraZeneca and Johnson \& Johnson) provide similar levels of
              protection in the first few months after vaccination against the wild type
              and the $\alpha$ variant (for details see Appendix~\ref{r.2.c}, starting
              on Page~\pageref{r.2.c}), which is the only time period and variant our
              simulations cover. Secondly, given the surprisingly good performance of
              rapid tests we tried to err on the side of being too optimistic with our
              modelling of vaccine performance. This is why we chose the perfect
              protection from vaccination for a large part of the population. Thirdly,
              reinfections are not a big issue for the time period that we look at. The
              incidences were small and the chance of more than one exposure to Covid
              are negligibly small. Thus, the value added by a probabilistic model of
              vaccination protection is very small for the period that we cover. }
\end{enumerate}
}

>>>>

\large{\textbf{\textcolor{red}{SUMMARY}}}

@@

              Furthermore, note that we only use the pre-pandemic diary data as the
              starting point. Contact restrictions and individual behavior adjustments
              reduce contacts. These are active throughout the period of analysis and
              they vary with the strictness of measures. In order to do so, it is crucial
              to take the type of contact into account; see for example our analysis of
              potential school closures on Page~\pageref{ref.2.a}. Closed schools mean
              that children have far fewer and parents have somewhat fewer contacts than
              without school closures.

@@

              We base our assumption on infectiousness being independent of age on
              \citet{Jones2021}. That study was the only one we could find that was able
              to differentiate between age differences in susceptibility (given a risk
              contact) vs. age differences in contact patterns. Moreover, they had fine
              grained age bins. That paper reports only slight differences in viral
              loads between German adults and children: ``The least infectious youngest
              children have 78\% (61, 94) of the peak culture probability of adults aged
              45 to 55''. Furthermore, they caution that these lower numbers may be due
              to different sample taking---such as the usage of smaller pediatric swab
              devices---rather than actual lower viral loads and conclude that the
              differences, if existent, are likely not clinically relevant. In fact,
              \citet{Goldstein2021}  reach similar conclusions, writing: \textit{``There
                  is limited evidence in the literature regarding age-related differences in
                  infectivity, although point estimates in several studies suggest that
                  infectivity may increase somewhat with age.''} We are thus confident that
              different assumptions in the range of plausible values would not
              change our results in a quantitatively meaningful way.

@@

              In our model, we thus simplify the way vaccines reduce transmission risk.
              In particular, we assume that that 75\% of individuals achieve sterile
              immunity through a vaccination while the remaining 25\% remain fully
              susceptible. Firstly, the existing evidence supports the
              assumption that all four vaccines approved in the EU (Biontech/Pfizer,
              Moderna, AstraZeneca and Johnson \& Johnson) provide similar levels of
              protection in the first few months after vaccination against the wild type
              and the $\alpha$ variant (for details see Appendix~\ref{r.2.c}, starting
              on Page~\pageref{r.2.c}), which is the only time period and variant our
              simulations cover. Secondly, given the surprisingly good performance of
              rapid tests we tried to err on the side of being too optimistic with our
              modelling of vaccine performance. This is why we chose the perfect
              protection from vaccination for a large part of the population. Thirdly,
              reinfections are not a big issue for the time period that we look at. The
              incidences were small and the chance of more than one exposure to Covid
              are negligibly small. Thus, the value added by a probabilistic model of
              vaccination protection is very small for the period that we cover. }
\end{enumerate}
}
